Exploring the ``Party City'' effect in the NBA

### 2017-03-28 eda_report.rnw
Added getAvgAge function, and incorporated log of avg.age into the model.

data[, list(meet.spread = mean(outcome == 'W'), .N), by = list(team, party)][order(team, party)]
@

@@

<<>>=
load(file = 'tmp_data/spreads_with_standings.RData')
model <- glm(outcome == 'W' ~ party + weekend + ndays.lgame + pct +
                 travel.dist + team + season + team:season,
             family = 'binomial', data = data)

>>>>

tmp <- data[, list(meet.spread = mean(outcome == 'W'), .N), by = list(team, party)][order(team, party)]

load(file = 'tmp_data/roster.RData')
roster[, season := gsub('-', '_', season)]
setkey(roster, team, season)
getAvgAge <- function(t, s, game.date, roster) {
    roster[.(t, s), mean(game.date - birthdate)]
}
data[, avg.age := getAvgAge(team, season, date, roster), by = list(team, season, date)]
data[, avg.age := as.numeric(avg.age) %>% log]

tmp <- data[, list(meet.spread = mean(outcome == 'W'), .N), 
            by = list(avg.age = round(avg.age), party, season)][order(avg.age, season, party)]
tmp[order(avg.age, party)]
## ages[, year := as.numeric(year)]
## data[, year := year(date)] # Note quite right.
## data <- merge(data, ages, by = c('team', 'year'), all.x = T)

@@

<<>>=
load(file = 'tmp_data/spreads_with_standings.RData')
model <- glm(outcome == 'W' ~ party + avg.age*party + weekend + ndays.lgame + pct +
                 travel.dist + team + season + team:season,
             family = 'binomial', data = data)
